Discrete Quantum Theories and Computing

### 2019-02-19 dissertation.tex
dissertation.lyx Acknowledgments Updates...

\item My other friends having an office in Lindley or \textportuges{Luddy}
Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Kaitlyn Owens, Praveen Narayanan,
Liang Chen (陈亮), \textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh,
Larry ``LP'' \textfrench{Ailes}, and Min-Chin Lin (林旻瑾), \ldots ,
etc.

>>>>

\item My other friends having an office in Lindley or \textportuges{Luddy}
Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Praveen Narayanan, Liang Chen (陈亮),
\textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh, Min-Chin Lin
(林旻瑾), and Career Services in the School of Informatics, Computing,
and Engineering, \ldots , etc.
